\begin{flushleft}
\hspace{0pt}
\vfill
    
    To Whom it may concern, 
\break
\newline
    Your presence at New Mexico Tech's Career Fair brought the NSA's internships to my attention. I believe my background in electronics and programming will make me a good candidate for the SIC program. I am currently an undergraduate student at New Mexico Tech majoring in astrophysics. I would like to get experience in a field more closely related to electrical engineering to help me decide if that is a better degree plan for me to choose. I have always been interested in working for NSA and look forward to future career opportunities at NSA. 
\break
\newline
    I have been working with electronics since 2014. My experience with building drones and other electronic devices has led me to have a moderate amount of experience with electronics and their design. I am currently taking an electronics lab at New Mexico Tech and will complete a second electronics lab second semester. I also have courses completed through calculus 3 and physics 2, through the end of this year I will be completing linear algebra, computational physics, and comprehensive physics. My background in programming comes from doing it as a hobby since 2014, some of my electronics projects have required some basic programming and I have built websites using PHP, MySQL, HTML, CSS, and JavaScript, I would consider myself beginner level in all languages. Through computational physics I am acquiring a large amount of experience with Python. I am always willing to learn and apply new languages and technologies to whatever problems I am faced with.
\break
\newline
    I can be contacted any time by email at bryanpeters43@gmail.com or by phone, 575-517-7370. 
\break
\newline
    Thank you for your time and consideration, I look forward to speaking to you about this internship opportunity.

\vfill
\hspace{0pt}
\end{flushleft}