\section{Background}
\par This project will focus on assisting the SSDS team with two different systems and a milestone test leading up to a spaceflight at some point in the future. The two systems are the alpha ChipSat, and the DeSCENT chip sattelites. The Alpha ChipSat is majorly completed -- final flight units are expected to be due in the very near future -- it is likely no major changes will be made. However, environemental testing still needs to be done on the flight units along with power and some reliability testing. These ChipSattelites will be the main communications interface on the light sail that CubeSat will be deploying. 

The DeSCENT mission is slightly different in comparison to the Alpha ChipSat. DeSCENT is the Demonstration of Suborbital Chipsats Ejected from New Shepard Test flight. Where the goal of this mission is to deploy a large number of chip satelites from Blue Origin's New Shepard launch vehicle. The New Shepard typically has an apogee of around 100-106km, just barely at the edge of space by international standards and well into space by U.S. standards.
After deploying these craft fall back down to earth, 
collecting and transmitting data like temperature, pressure, vehicle orientation etc the entire time.
Under ideal conditions these chipsats will be communicating their location to us once on the ground, allowing for at least one or two recoveries. However there are a lot of factors at play for that to happen out of one hundred we can likely hope for 3-4 to be recovered. 